---
title: 'PragmaticQA E4: Prior Sensitivity Free Production'
author: "PT"
date: "2024-04-30"
output: github_document
---

```{r, include=FALSE}
library(tidyverse)
library(tidyboot)
library(aida)
library(brms)
library(tidybayes)
library(cspplot)
```

```{r, include=FALSE}
# these options help Stan run faster
options(mc.cores = parallel::detectCores())
```

# Intro

This is another experiment in the PragmaticQA project, wherein we investigate whether speakers' overinformativeness in response to polar questions depends on the (commonly known) prior probability of the available options. The live experiment can be found [here](https://magpie-ea.github.io/magpie3-qa-overinfo-free-production/experiments/04-priorSensitivity_free_production/). We manipulate the prior probability of the available options in context, resulting in two critical conditions, highPrior (high prior options available) and lowPrior (high prior option not available).
The experiment is a free production experiment. Each participant sees four main trials (two per condition, assigned at random to four randomly chosen vignettes), and one filler trial. Fillers are re-used from CogSci E1.

* Pilot 1: five vignettes only were chosen here: cardBlanche, icecreamFlavors, streamingOptions, coffeeShops, socialMedia. N=30 were recruited.

```{r, include=FALSE, message=FALSE}
d <- read_csv("data/results_PragmaticQA-E3-priorSensitivity-pilot-1.csv")
# number of recruited subjects
cat("Number of recruited subjects: ", d %>% pull(submission_id) %>% unique() %>% length())

# attention check based exclusions
# check attention check completion
df_attention <- d %>% filter(trial_type == "filler") %>% rowwise() %>%
  mutate(passed_trial = grepl(tolower(correct_response), tolower(answer))) 

df_attention_fail <- df_attention %>% group_by(submission_id) %>% 
  mutate(passed_subj = sum(passed_trial) > 0)

# participants who failed attention checks 
subj_id_attention_fails <- df_attention_fail %>% filter(passed_subj == FALSE) %>% pull(submission_id) %>% unique()
cat("Subjects who failed attention checks: ", subj_id_attention_fails)  
cat("Number of subjects who failed attention checks: ", length(subj_id_attention_fails))

# filtering out main trials only and only subjects who passed attention checks
d_main <- d %>% filter(!(submission_id %in% subj_id_attention_fails)) %>% 
  filter(condition != "filler")
```

The freely typed responses were manually categorized into the following categories:

* "taciturn": responses just saying "yes" or "yes, we do" or similar.
* "taciturn_more": responses saying "yes" but providing some additional information without mentioning specific options, for instance "Yes there are some coffee shops around the corner"
* "mostLikely": response mentioning the most likely option among the available ones, e.g., "Yes we do, we have 3 flavours the chocolate delight is the favourite of them"
* "fullList": responses mentioning the two specific available options, e.g., "Sure, we've got Chocolate Delight and Strawberry Swirl"
* "exceptive: responses mentioning which option is NOT available, e.g., "Yes, all except Card Blanche"

Below the single category proportions are displayed by condition.
```{r}
df_answerOptions_global_summary <- d_main %>% 
  group_by(category) %>% 
  summarise(answerType_count = n(), 
            answerType_proportion = answerType_count / nrow(d)
            )

df_answerOptions_byCondition_summary <- d_main %>% 
  group_by(condition) %>%
  mutate(condition_counts = n()) %>%
  group_by(category, condition) %>% 
  summarise(answerType_count = n(), 
            answerType_proportion = answerType_count / condition_counts
            ) %>% unique()


df_answerOptions_byCondition_summary %>%
  ggplot(aes(x = condition, y = answerType_proportion, fill = category)) +
  geom_col(color = "#575463") +
  theme_csp() +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab("Proportion of answer type") +
  xlab("") 
```

The main hypothesis is that speakers will be more overinformative in the low prior condition; i.e., they will produce more responses of categories exceptive, fullList, taciturn_more, mostLikely. This binarized distinction is used to plot "overinformativeness" proportions by-condition below:

```{r, include=FALSE}
d_main_binary_summary <- d_main %>% 
  mutate(is_overinformative = ifelse(category != "taciturn", 1, 0)) %>%
  group_by(condition) %>% 
  tidyboot_mean(column = is_overinformative)
```

We see that the difference is not very large.
```{r}
d_main_binary_summary %>%
  ggplot(., aes(x = condition, y = mean, ymin=ci_lower, ymax=ci_upper)) +
  geom_col() +
  geom_errorbar(width = 0.4) +
  ylim(0, 1)
```