---
title: "QA free typing analysis"
author: "Polina Tsvilodub"
date: '2023-01-02'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(tidyboot)
library(brms)
library(tidybayes)
library(ggpattern)
library(cspplot)
```

```{r, include=FALSE}
# these options help Stan run faster
options(mc.cores = parallel::detectCores())
```


## Load processed experimental results and neural model data, display descriptions


```{r, include=FALSE, warning=FALSE, message=FALSE}
answerOrder <- c( 'competitor', 'sameCategory', 'otherCategory', 'fullList', 'taciturn', 'other')

e1_humans <- read_csv("../data/results_QA-overinfo-freeTyping-cogsci_full_anonymized_categorized_cleaned.csv") %>% select(category, answer, itemName) %>% # results_QA_e1_cleaned.csv
  mutate(prompt = "human E1") %>% rename("predictions" = "answer")

e2_humans <- read_csv("../../data_paper_neural/e2_human_summary_wide.csv") %>% 
  mutate(prompt = "human E2")
e2_human_byCategory <- read_csv("../data/results_e2_human_category_raw_cleaned.csv")
e2_items_cats <- read_csv("../../data_paper_neural/e2_ItemCategorization.csv") 
e2_vignettes <-  read_csv("../../data_paper_neural/e2_vignettes.csv")


nm_samples_categorized_e1 <- read_csv("../../data_paper_neural/QA_neural_models_categorized_samples_E1.csv") #("../supplementary_materials/QA_neural_models_categorized_samples_E1.csv") 
nm_samples_categorized_e2 <- read_csv("../../data_paper_neural/QA_neural_models_categorized_samples_E2.csv")#("../supplementary_materials/QA_neural_models_categorized_samples_E2.csv")

e1_samples_global <- nm_samples_categorized_e1 %>%
  select(-probs, -is_few_shot, -dataset, -model_type) %>%
  rename("prompt" = "model_name") %>%
  rbind(., e1_humans)

e1_gpt3_summary <- read_csv("../../data_paper_neural/e1_gpt3_byPrompt_summary.csv")

e2_gpt3_category_summary <- read_csv("../../data_paper_neural/e2_gpt3_byPrompt_byCategory_summary.csv")
e2_gpt3_context_summary <- read_csv("../../data_paper_neural/e2_gpt3_byPrompt_byContext_summary.csv")

e2_samples_global <- nm_samples_categorized_e2 %>% select(-probs, -is_few_shot, -dataset, -model_type) %>%
  rename("prompt" = "model_name") %>%
  rbind(., e2_human_byCategory %>% select(-submission_id, -settingName, -response_option) %>% mutate(prompt = "human E2") %>% rename("predictions" = "answer"))
```


Post-Cogsci prompting exploration:
```{r}
e2_cot_mimatch <- read_csv("../../code/results/GPT3-davinci-003-samples-oneShotLearner-CoT-mismatch-e2.csv") %>% 
  filter(!is.na(response_option)) %>%
  left_join(., read_csv("../../data_paper_neural/e2_vignettes.csv"), by="itemName") %>%
  group_by(context_nr) %>%
  mutate(num_response_context = n()) %>%
  separate_rows(response_option, sep=",") %>%
  mutate(response_option = gsub(" ", "", response_option),
         prompt = "mismatch CoT"
         ) %>%
  left_join(., read_csv("../../data_paper_neural/e2_ItemCategorization.csv"), by="response_option")

e2_cot_mismatrch_category_summary <- read_csv("../../code/results/GPT3-davinci-003-samples-oneShotLearner-CoT-mismatch-e2.csv") %>% 
  filter(!is.na(response_option)) %>%
  mutate(n_response = n()) %>%
  group_by(category) %>%
  summarize(prop = n() / n_response) %>% unique() %>% 
  mutate(prompt = "mismatch CoT")
  
e2_qa_mimatch <- read_csv("../../code/results/GPT3-davinci-003-samples-oneShotLearner-QA-mismatch-e2.csv") %>% 
  filter(!is.na(response_option)) %>%
  left_join(., read_csv("../../data_paper_neural/e2_vignettes.csv"), by="itemName") %>%
  group_by(context_nr) %>%
  mutate(num_response_context = n()) %>%
  separate_rows(response_option, sep=",") %>%
  mutate(response_option = gsub(" ", "", response_option),
         prompt = "mismatch QA"
         ) %>%
  left_join(., read_csv("../../data_paper_neural/e2_ItemCategorization.csv"), by="response_option")

e2_qa_mismatrch_category_summary <- read_csv("../../code/results/GPT3-davinci-003-samples-oneShotLearner-QA-mismatch-e2.csv") %>% 
  filter(!is.na(response_option)) %>%
  mutate(n_response = n()) %>%
  group_by(category) %>%
  summarize(prop = n() / n_response) %>% unique() %>% 
  mutate(prompt = "mismatch QA")

e2_cot_mismatch_summary <- e2_cot_mimatch %>% ungroup() %>% group_by(context_nr, global_category) %>%
  summarize(n_responseType = n(), prop = n_responseType / num_response_context) %>% unique() %>%
  filter(!is.na(global_category)) %>% select(-n_responseType) %>%
  pivot_wider(values_from = prop, names_from = context_nr) %>%
  mutate(prompt = "mismatch CoT")  

e2_qa_mismatch_summary <- e2_qa_mimatch %>% ungroup() %>% group_by(context_nr, global_category) %>%
  summarize(n_responseType = n(), prop = n_responseType / num_response_context) %>% unique() %>%
  filter(!is.na(global_category)) %>% select(-n_responseType) %>%
  pivot_wider(values_from = prop, names_from = context_nr) %>%
  mutate(prompt = "mismatch QA")

e2_mismatch_summary <- rbind(e2_cot_mismatch_summary, e2_qa_mismatch_summary)

e2_mismatch_category_summary <- rbind(e2_qa_mismatrch_category_summary, e2_cot_mismatrch_category_summary)
```


### Comparing neural and human responses

```{r}
# retrieve ChatGPT by context results

nm_samples_categorized_e1 %>% filter(model_name == "chatGPT") %>%
  filter((category != 'yes')) %>%
  group_by(model_name, category, is_few_shot) %>%
  mutate(n = n()) %>% ungroup() %>% group_by(is_few_shot) %>%
  mutate(cat_n = n(),
    prop = n / cat_n) %>%
  select(model_name, is_few_shot, category, prop) %>% unique()

nm_samples_categorized_e2 %>% filter(model_name == "chatGPT") %>%
  filter((category != 'yes')) %>%
  group_by(model_name, category, is_few_shot) %>%
  mutate(n = n()) %>% ungroup() %>% group_by(is_few_shot) %>%
  mutate(cat_n = n(),
    prop = n / cat_n) %>%
  select(model_name, is_few_shot, category, prop) %>% unique()
```



## Stats

Compute p-value of human data under model data: Chi-square tests of human response proportions vs model probabilities and response proportions (assumed to be ground truth).

```{r, warning=FALSE, message=FALSE}
e1_samples_global <- e1_samples_global %>% mutate(
  category = factor(category, levels = c("competitor", "sameCategory", "otherCategory", "fullList", "other", "taciturn"))
)
e1_samples_global_model_summary <- e1_samples_global %>% filter(prompt != "human E1") %>%
  group_by(prompt) %>% mutate(resp_count = n()) %>% group_by(prompt, category) %>% summarise(cat_count = n(), prop = cat_count / resp_count) %>% unique()
# assumed order of counts / proportions: comp, sameCat, otherCat, fullList, other, taciturn
human_counts_e1 <- e1_samples_global %>% filter(prompt == "human E1") %>% group_by(category) %>%
  summarize(count = n()) 

e1_gpt3_summary_pval <- e1_gpt3_summary %>% filter(prompt != "human E1") %>% 
  mutate(category = factor(category, levels = c("competitor", "sameCategory", "otherCategory", "fullList", "other", "taciturn")))

compute_p <- function(human_counts, name, models_df, type) {
  cats <- c("competitor", "sameCategory", "otherCategory", "fullList", "other", "taciturn")
  
  if (type == "samples") {
    df <- models_df %>% filter(prompt == name) %>% select(category, prop) 
  } else {
    df <- models_df %>% filter(prompt == name) %>% select(category, answer_type_prob) %>%
      rename("prop" = "answer_type_prob") 
  }
  df <- df %>% filter(!is.na(category))
  answer_types <- df$category
  # pad missing category with epsilon and renormalize
  if (answer_types %>% length() < 6) {
    for (a in setdiff(cats, answer_types)) {
      df <- df %>% ungroup() %>%
      add_row(category = a, prop = 0.01)
    }
  }
  df <- df %>% ungroup() %>% mutate(
        category = factor(category, levels = c("competitor", "sameCategory", "otherCategory", "fullList", "other", "taciturn")),
        sum_prop = sum(prop),
        prop = prop / sum_prop
      )  #%>% filter(!is.na(category))
  df <- human_counts %>% left_join(., df, by = "category")
  print(df)
  print(df %>% pull(count))
  print(df %>% pull(prop))
  res <- chisq.test(x = df %>% pull(count), p = df %>% pull(prop), rescale.p = TRUE)
  return(res$p.value)
}

all_models_samples_e1 <- e1_samples_global_model_summary %>% pull(prompt) %>% unique()
# define df 
df_pvals_models_vs_humans_e1 <- data.frame(model_name=character(), type=character(), p=double())
# iterate over model samples
for (m in all_models_samples_e1) {
  print(m)
  p <- compute_p(human_counts_e1, m, e1_samples_global_model_summary, "samples")
  df_pvals_models_vs_humans_e1 <- df_pvals_models_vs_humans_e1 %>%
    add_row(model_name=m, type="samples", p=p)
}
# iterate over scores
all_gpt3_models <- e1_gpt3_summary_pval %>% pull(prompt) %>% unique()
for (m in all_gpt3_models) {
  p <- compute_p(human_counts_e1, m, e1_gpt3_summary_pval, "samples")
  df_pvals_models_vs_humans_e1 <- df_pvals_models_vs_humans_e1 %>%
    add_row(model_name=m, type="prob", p=p)
}
cat("P values under Chi square tests of human data against probabilities / sample proportions of neural models ")
df_pvals_models_vs_humans_e1
```

```{r}
all(df_pvals_models_vs_humans_e1 %>% pull(p) < 0.05)
```

The same analysis for E2:
```{r, warning=FALSE, message=FALSE}
e2_samples_global <- e2_samples_global %>% mutate(
  category = factor(category, levels = c("competitor", "mostSimilar", "sameCategory", "otherCategory", "fullList", "other", "taciturn"))
) 
e2_samples_global_model_summary <- e2_samples_global %>% filter(prompt != "human E2") %>% filter(!is.na(category)) %>%
  group_by(prompt) %>% mutate(resp_count = n()) %>% group_by(prompt, category) %>% summarise(cat_count = n(), prop = cat_count / resp_count) %>% unique()
# assumed order of counts / proportions: comp, sameCat, otherCat, fullList, other, taciturn
human_counts_e2 <- e2_samples_global %>% filter(prompt == "human E2") %>% group_by(category) %>%
  summarize(count = n()) 

e2_gpt3_summary_pval <- e2_gpt3_category_summary %>% filter(prompt != "human E2") %>% 
  mutate(category = factor(category, levels = c("competitor", "mostSimilar", "sameCategory", "otherCategory", "fullList", "other", "taciturn")))

compute_p <- function(human_counts, name, models_df, type) {
  cats <- c("competitor", "mostSimilar", "sameCategory", "otherCategory", "fullList", "other", "taciturn")
  
  if (type == "samples") {
    df <- models_df %>% filter(prompt == name) %>% select(category, prop) 
  } else {
    df <- models_df %>% filter(prompt == name) %>% select(category, answer_type_prob) %>%
      rename("prop" = "answer_type_prob") 
  }
  df <- df %>% filter(!is.na(category))
  answer_types <- df$category
  # pad missing category with epsilon and renormalize
  if (answer_types %>% length() < 7) {
    for (a in setdiff(cats, answer_types)) {
      df <- df %>% ungroup() %>%
      add_row(category = a, prop = 0.01)
    }
  }
  df <- df %>% ungroup() %>% mutate(
        category = factor(category, levels = c("competitor", "mostSimilar", "sameCategory", "otherCategory", "fullList", "other", "taciturn")),
        sum_prop = sum(prop),
        prop = prop / sum_prop
      )  
  df <- human_counts %>% left_join(., df, by = "category")
  print(df)
  print(df %>% pull(count))
  print(df %>% pull(prop))
  res <- chisq.test(x = df %>% pull(count), p = df %>% pull(prop), rescale.p = TRUE)
  return(res$p.value)
}

all_models_samples_e2 <- e2_samples_global_model_summary %>% pull(prompt) %>% unique()
# define df 
df_pvals_models_vs_humans_e2 <- data.frame(model_name=character(), type=character(), p=double())
# iterate over model samples
for (m in all_models_samples_e2) {
  print(m)
  p <- compute_p(human_counts_e2, m, e2_samples_global_model_summary, "samples")
  df_pvals_models_vs_humans_e2 <- df_pvals_models_vs_humans_e2 %>%
    add_row(model_name=m, type="samples", p=p)
}
# iterate over scores
all_gpt3_models_e2 <- e2_gpt3_summary_pval %>% pull(prompt) %>% unique()
for (m in all_gpt3_models_e2) {
  p <- compute_p(human_counts_e2, m, e2_gpt3_summary_pval, "samples")
  df_pvals_models_vs_humans_e2 <- df_pvals_models_vs_humans_e2 %>%
    add_row(model_name=m, type="samples", p=p)
}
cat("P values under Chi square tests of human data against probabilities / sample proportions of neural models ")
df_pvals_models_vs_humans_e2
```

```{r}
all(df_pvals_models_vs_humans_e2 %>% pull(p) < 0.05)
```

### Plot

Experiment 1:
```{r}
e1_plot_summary_labels <- e1_gpt3_summary %>% group_by(category) %>%
  summarize(max_val = max(prop)) %>% 
  mutate(category = factor(category, levels = c("competitor", "sameCategory", "otherCategory", "fullList", "other", "taciturn"), labels = c("competitor\n(iced coffee)", "similar option\n(soda)", "unrelated\noption\n(Chardonnay)", "all options", "other", "no options") ))

e1_gpt3_summary %>% 
  mutate(prompt = factor(prompt, levels = c("zero-shot", "one-shot Explanation", "one-shot QA", "one-shot CoT", "human E1")),
    category = factor(category, levels = rev(c("taciturn", "other", "fullList", "otherCategory", "sameCategory", "competitor")), labels = rev(c("no options",  "other", "all options", "unrelated\noption\n(Chardonnay)", "similar option\n(soda)", "competitor\n(iced coffee)"  ) ))) %>%
  ggplot(., aes(x = category, y = prop, fill = prompt, label = category)) +
  geom_col(position = position_dodge(preserve = "single"), color = "#575463", width = 0.8 )+
  geom_text(inherit.aes = FALSE, data = e1_plot_summary_labels, aes(x = category, y = max_val, label = category), stat = 'unique', nudge_y = 0.08, size = 4, check_overlap = TRUE) +
  theme_csp() +
  scale_y_continuous( limits = c(0, 0.7), breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
   theme(plot.title = element_text(hjust = 0.5), legend.position = "right",  legend.title = element_text(size=12), legend.text = element_text(size=12), axis.text.x = element_blank(), axis.ticks.x = element_blank() ) +  
  ylab("Proportion of answer type") +
  xlab("Answer type") +
  ggtitle("Do you have iced tea?")
```
Post-review stacked version of the plot:
```{r}
e1_gpt3_summary %>% 
  mutate(prompt = factor(prompt, levels = c("zero-shot", "one-shot Explanation", "one-shot QA", "one-shot CoT", "human E1"), 
                         labels = c("zero-shot\n(V)", "one-shot\nExplanation\n(I+II+IV+V)", "one-shot\nQA\n(I+III+IV+V)", "one-shot\nCoT\n(I-V)", "human\nE1\n(V)")),
    category = factor(category, levels = rev(c("taciturn", "other", "fullList", "otherCategory", "sameCategory", "competitor")), labels = rev(c("no options",  "other", "all options", "unrelated option\n(Chardonnay)", "similar option\n(soda)", "competitor\n(iced coffee)"  ) ))) %>%
  ggplot(., aes(x = prompt, y = prop, fill = category, label = category)) +
  geom_col(color = "#575463", show.legend = F)+ # , aes(linetype=prompt), size = 1, show.legend = F
  #geom_text(inherit.aes = FALSE, data = e1_plot_summary_labels, aes(x = category, y = max_val, label = category), stat = 'unique', nudge_y = 0.08, size = 4, check_overlap = TRUE) +
  theme_csp() +
  scale_y_continuous( limits = c(0, 1), breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
   theme(plot.title = element_text(hjust = 0.5), legend.position = "right",  legend.title = element_text(size=12), legend.text = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_text(angle = 35),
    panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    #panel.grid.major = element_blank(), #remove major gridlines
    #panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent') #transparent legend panel
         ) +  
  ylab("Proportion of answer type") +
  xlab("Prompt type") +
  guides(fill=guide_legend(title="Response category")) +
  ggtitle("Do you have iced tea?")

#ggsave("../viz/revisions/E1_stacked_numbered_transparent.pdf", bg="transparent", width = 5, height = 4.5)
```


Experiment 2:

```{r}
e2_gpt3_context_summary %>%
#e2_mismatch_summary %>% 
  mutate(prompt = factor(prompt, levels = c("zero-shot", "one-shot Explanation", "one-shot QA", "one-shot CoT", "human E2"))) %>%
  #mutate(prompt = factor(prompt, levels = c("mismatch QA", "mismatch CoT"))) %>%
  mutate(global_category = factor(global_category, levels = c( 'otherCategory', 'mostSimilar', 'competitor_c2', 'competitor_c1'),
                           labels = c("unrelated option\n(carpet)", "a priori\nsimilar (pillow)", "competitor 2\n(bubble wrap)", "competitor 1\n(sleeping bag)")
                           )) %>%
  ggplot(., aes(fill = prompt, x = global_category)) +
  geom_col(aes(y = context1), position = position_dodge(preserve = "single"), color = "#575463" ) +
  geom_col(aes(y = -context2), position = position_dodge(preserve = "single"), color = "#575463" ) +
  theme_csp() + 
  theme( axis.text.y = element_text(size = 12), axis.text.x = element_text(size = 12),  legend.title = element_text(size=12), legend.text = element_text(size=12), legend.position = "right", plot.title = element_text(hjust = 0.5),
         panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    #panel.grid.major = element_blank(), #remove major gridlines
    #panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent') #transparent legend panel
         ) + # , axis.ticks.y = element_blank(), 
  scale_y_continuous( limits = c(-1, 1), breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("1", "0.5", "0", "0.5", "1")) +
  geom_hline(yintercept = 0, color = "white", size = 1) +
  coord_flip() +
  ylab("mirror transport <--> sleepover") +
  xlab("") +
  ggtitle("Do you have a blanket?")

#ggsave("../viz/revisions/E2_transparent.pdf", bg="transparent", width = 7.5, height = 4.5)

```

Post-review revisions (stacked plot for E2):
```{r}
e2_gpt3_context_summary_stack <- e2_gpt3_context_summary %>% 
  rowwise() %>%
  mutate(context_sum = sum(context1+context2),
         context1_prop = context1 / context_sum,
         context2_prop = context2 / context_sum
         ) %>%
  pivot_longer(cols = c(context1_prop, context2_prop), names_to = "byContext_prop_key", values_to = "byContext_prop_val")

e2_gpt3_context_summary_stack %>%
#e2_mismatch_summary %>% 
  mutate(prompt = factor(prompt, levels = c("zero-shot", "one-shot Explanation", "one-shot QA", "one-shot CoT", "human E2"))) %>%
  #mutate(prompt = factor(prompt, levels = c("mismatch QA", "mismatch CoT"))) %>%
  mutate(global_category = factor(global_category, levels = c( 'otherCategory', 'mostSimilar', 'competitor_c2', 'competitor_c1'),
                           labels = c("unrelated option\n(carpet)", "a priori\nsimilar (pillow)", "competitor 2\n(bubble wrap)", "competitor 1\n(sleeping bag)")
                           ),
         byContext_prop_key = factor(byContext_prop_key, levels = c("context2_prop", "context1_prop"), labels = c( "transportation", "sleepover") )
         ) %>%
  ggplot(., aes(fill = byContext_prop_key, x = global_category)) +
  geom_col(aes(y = byContext_prop_val), color = "#575463" ) +
  #geom_col(aes(y = -context2), color = "#575463" ) +
  theme_csp() + 
  theme( axis.text.y = element_text(size = 10), axis.text.x = element_text(size = 8, angle = 35),  legend.title = element_text(size=12), legend.text = element_text(size=12), legend.position = "right", plot.title = element_text(hjust = 0.5), strip.text.x = element_text(size = 10)) + # , axis.ticks.y = element_blank(), 
  #scale_y_continuous( limits = c(-3, 3), ) + # breaks = c(-1, -0.5, 0, 0.5, 1), labels = c("1", "0.5", "0", "0.5", "1")
  #geom_hline(yintercept = 0, color = "white", size = 1) +
  #coord_flip() +
  facet_grid(.~prompt) +
  ylab("By-context proportion") +
  xlab("Response category") +
  guides(fill=guide_legend(title="Context")) +
  ggtitle("Do you have a blanket?")

#ggsave("../viz/revisions/E2_stacked_byPrompt.pdf", width = 11.5, height = 4.5)
```

The same thing but without faceting, using different styles instead:
```{r}

e2_gpt3_context_summary_stack %>% ungroup() %>%
  mutate(model_type = factor(model_type, levels = c("extractive", "generative"))) %>%
  ggplot(aes(x = answerType, fill = answerType, y = prop, pattern = model_type)) +
  geom_col_pattern(alpha = 0.7, position = position_dodge(preserve = "single"),
                   width = bar.width,
                   color = "black", 
                   pattern_fill = "black",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.025,
                   pattern_key_scale_factor = 0.6
                   ) +
  scale_pattern_manual(values = c(extractive = "stripe", generative = "none")) +
  labs(x = "Answer type", y = "Response type proportion", pattern = "Model type") +
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none"))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(strip.text.x = element_text(size = 10)) +
  theme(panel.spacing = unit(3, "lines")) +
  ggtitle("Response type proportions by model type (extractive vs generative)")
```  


Post-Cogsci mismatching prompt explorations:
```{r}
e2_mismatch_category_summary %>% 
  mutate(prompt = factor(prompt, levels = c("mismatch QA", "mismatch CoT")),
    category = factor(category, levels = rev(c("taciturn", "other", "fullList", "otherCategory", "mostSimilar", "sameCategory", "competitor")), labels = rev(c("no options",  "other", "all options", "unrelated\noption\n(carpet)", "most similar\n(pillow)", "similar option\n(bubble wrap)", "competitor\n(sleeping bag)"  ) ))) %>%
  ggplot(., aes(x = category, y = prop, fill = prompt, label = category)) +
  geom_col(position = position_dodge(preserve = "single"), color = "#575463", width = 0.8 )+
  theme_csp() +
  scale_y_continuous( limits = c(0, 0.7), breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
   theme(plot.title = element_text(hjust = 0.5), legend.position = "right",  legend.title = element_text(size=12), legend.text = element_text(size=12), axis.text.x = element_text(angle = 45) ) +  
  ylab("Proportion of answer type") +
  xlab("Answer type") +
  ggtitle("Do you have a blanket?")
```